### 2021-04-16 doc/manuscript/Dow_SI.Rmd
update hypotheses & schematic_summary
add draft tree rings figure to manuscript
#49

# SUPPLEMENTARY INFO (copied from Dow_manuscript.Rmd)
##SI table numbers
table_species="S1"  
sample_size_by_year= "S2"
mean_growth_parameters_table="S3"

@@

>>>>

# SUPPLEMENTARY INFO (copied from Dow_manuscript.Rmd)
##SI table numbers
table_species="S1"  
sample_size_by_year= "S2"
mean_growth_parameters_table="S3" 
chronologies_table="S4"

@@

\newpage
# (placeholder for Table S4-- chronologies table.)

### 2021-04-16 doc/manuscript/Dow_manuscript_Nature.Rmd
knit in latest fig
add draft tree rings figure to manuscript
#49

*Grant Harley (ASSUMING WE USE SMOKIES TREE RING RECORDS)*

@@

DOYtiming_caption <- "Figure 3 | Leaf (a,b) and stem growth (c,d) phenology at the Smithsonian Conservation Biology Institute (a,c) and Harvard Forest (b,d) from 1998 to 2020 (when available). **DRAFT FIGURE-- REAL DATA BUT NEEDS FORMATTING.** Panels (a-b) show leaf phenology... Panels (c-d) show the dates at which stem growth milestones were acheived, on average, for sampled populations of ring-porous and diffuse-porous trees at each site. Mean temperature was calculated for each wood-type/site combination over the respective critical $T_{max}$ window, then turned into a ratio and assigned a color on a gradient where the coldest year in the sample is blue and the warmest is red."

tree_rings_caption <- "Figure 4 | Climate sensitivity of annual growth, as derived from tree-rings, for dominant ring- and diffuse- porous species at the Smithsonian Conservation Biology Institute and Harvard Forest. Shown are Pearson correlations between ring-width index and and monthly Tmax. Species codes are as given in Table 2.(THIS FIGURE WILL PROBABLY BE PROBABLY MODIFIED SIGNFICANTLY TO INCLUDE LOTS MORE SITES.)"

# SUPPLEMENTARY INFO (this chunk must be repeated in Dow_SI.Rmd)
##SI table numbers
table_species="S1"  
sample_size_by_year= "S2"
mean_growth_parameters_table="S3"

@@

```{r tree_rings, out.width="100%", echo=FALSE, fig.align="center", fig.cap= tree_rings_caption}
knitr::include_graphics("tables_figures/tree_cores_tmax.tif")
```

>>>>

*Grant Harley*

@@

DOYtiming_caption <- "Figure 3 | Leaf (a,b) and stem growth (c,d) phenology at the Smithsonian Conservation Biology Institute (a,c) and Harvard Forest (b,d) from 1998 to 2020 (when available). Panels (a-b) show leaf phenology... Panels (c-d) show the dates at which stem growth milestones were acheived, on average, for sampled populations of ring-porous and diffuse-porous trees at each site. Mean temperature was calculated for each wood-type/site combination over the respective critical $T_{max}$ window, then turned into a ratio and assigned a color on a gradient where the coldest year in the sample is blue and the warmest is red."

tree_rings_caption <- "Figure 4 | Sensitivity of annual growth, as derived from tree-rings, to monthly maximum temperatures, for ## chronologies from ## sites across eastern North America. Chronologies are grouped by xylem porosity and ordered by mean April T_max. Chronology details are given in Table S4. (NOTE: Figure still needs some work. See [GitHub Issue #49](https://github.com/EcoClimLab/growth_phenology/issues/49).)"

# SUPPLEMENTARY INFO (this chunk must be repeated in Dow_SI.Rmd)
##SI table numbers
table_species="S1"  
sample_size_by_year= "S2"
mean_growth_parameters_table="S3" 
chronologies_table="S4"

@@

```{r tree_rings, out.width="100%", echo=FALSE, fig.align="center", fig.cap= tree_rings_caption}
knitr::include_graphics("tables_figures/tree_rings_tmax.png")
```
